### 2021-12-10 thesis/tex/oscillations.tex
update

\subsection{The Mixing Matrix}
Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the expression for the weak charged current, we get
\begin{align}\label{eq:j_CC2}
    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
\end{align}
Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$. 
Thus, neutrino interactions still conserve lepton number.
However, the Higgs-lepton Yukawa Lagrangian 
in Eq.~\ref{eq:L_H} violates lepton number conservation since it couples the charged lepton flavor $\alpha$ to the neutrino mass eigenstate $k$, which is a superposition of flavors. 
There is no transformation that leaves both the interaction and kinetic Lagrangian invariant, thus violating this symmetry.

@@

We construct the PMNS matrix by parametrizing it as as
\begin{align}\label{PMNS_def}
    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12}P_{Maj} \nonumber \\
     &= \begin{pmatrix}
        U_{e 1} & U_{e2} & U_{e3} \\
         U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
         U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
      \end{pmatrix} \nonumber \\
      & = \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
\begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}
\begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}
\nonumber \\
 &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 
        -s_{12} c_{23}-c_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{12} c_{23}-s_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & s_{23} c_{13} \\ 
        s_{12} s_{23}-c_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}}  & -c_{12} s_{23}-s_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{23} c_{13}
    \end{pmatrix}
    \begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda{2}} & 0 \\ 0 & 0 & e^{i \lambda{3}}\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \lambda{i},\delta_\mathrm{CP} \leq 2\pi$.

By construction, it provides the unitary transformation between the flavor and mass bases.
Any unitary $3\times3$ matrix can be parametrized using three angles and six phases. However, not all phases affect the 
charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
leaving only one physical phase for us to measure: one term in the form of a Dirac CP-violating phase $\delta_\mathrm{CP}$.
However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
Thus, we include two Majorana phases $\lambda{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.

@@

The three-neutrino oscillation Hamiltonian from Eq.~\eqref{eq:H_3gen}
now reduces to 
\begin{align}
    H_F &= \frac{1}{2E}(U M^2 U^\dagger + A) \nonumber \\
        &= \frac{1}{2E}\left[U \begin{pmatrix}
            0 & 0 & 0 \\
            0 & \dm_{21} & 0 \\
            0 & 0 & 0
        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
            1 & 0 & 0 \\
            0 & 0 & 0 \\
            0 & 0 & 0
        \end{pmatrix}\,. 
\end{align}
The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified. The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane. Thus, the reduced mass matrix $\mathbb{M}_{12}$ commutes with $R_{13}$. Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathbb{M}_{12}$.
Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
\begin{align}
    \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
\end{align}
Thus,
\begin{align}
    U \mathbb{M}_{12} U^\dagger &=
    R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
    &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
    &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
\end{align}
And due to the fact that the rotation matrices are unitary,
\begin{align}
    R\,R^\dagger = \mathbb{I}\,,
\end{align}
we have that 
\begin{align}
    U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
    &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
    &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
\end{align}
We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
\begin{align}
    U &= R_{12}
\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
\end{align}

Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
\begin{align}
    H_F
        &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
            0 & 0 & 0 \\
            0 & \dm_{21} & 0 \\
            0 & 0 & 0
        \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
            1 & 0 & 0 \\
            0 & 0 & 0 \\
            0 & 0 & 0
        \end{pmatrix} \nonumber \\
        &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
            0 & 0 & 0 \\
            0 & \dm_{21} & 0 \\
            0 & 0 & 0
        \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
            1 & 0 & 0 \\
            0 & 0 & 0 \\
            0 & 0 & 0
        \end{pmatrix}\,. 
\end{align}

We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:

@@

\subsection{Earth propagation}
We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
symmetric piecewise polynomials for the Earth density in \si{\gram\cm^3} shown in the left panel of Fig.~\ref{fig:potential}.
We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
oscillations.

Using a value of $Y=0.5$ electron per nucleon, we express the matter potential as
\begin{align}
    V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
           &= \SI{3.8e-23}{\eV} \times \rho\,,
\end{align}
a low number due to the smallness of $G_F$. This is plotted in the right panel of Fig.~\ref{fig:potential}
\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/potential.pdf}
    \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
    \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
    \caption{}\label{fig:oscillations}
\end{figure}

>>>>

\subsection{The Mixing Matrix}
Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the expression for the weak charged current, we get
\begin{align}\label{eq:j_CC2}
    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
\end{align}

@@

We construct the PMNS matrix by parametrizing it as as
\begin{align}\label{PMNS_def}
    U &= R_{23}R_{13,\delta_{\text{CP}}}R_{12}P_{Maj} \nonumber \\
     &= \begin{pmatrix}
        U_{e 1} & U_{e2} & U_{e3} \\
         U_{\mu 1} & U_{\mu 2} & U_{\mu 3} \\
         U_{\tau 1} & U_{\tau 2} & U_{\tau 3}
      \end{pmatrix} \nonumber \\
      & = \begin{pmatrix}1 & 0 & 0 \\ 0 & c_{23} & s_{23} \\ 0 & -s_{23} & c_{23}\end{pmatrix}
\begin{pmatrix}c_{13} & 0 & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 0 & 1 & 0 \\ -s_{13} e^{i \delta_{\mathrm{CP}}} & 0 & c_{13}\end{pmatrix}
\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1\end{pmatrix}
\begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda_{2}} & 0 \\ 0 & 0 & e^{i \lambda_{3}}\end{pmatrix}
\nonumber \\
 &=\begin{pmatrix}c_{12} c_{13} & s_{12} c_{13} & s_{13} e^{-i \delta_{\mathrm{CP}}} \\ 
        -s_{12} c_{23}-c_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{12} c_{23}-s_{12} s_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & s_{23} c_{13} \\ 
        s_{12} s_{23}-c_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}}  & -c_{12} s_{23}-s_{12} c_{23} s_{13}e^{i \delta_{\mathrm{CP}}} & c_{23} c_{13}
    \end{pmatrix}
    \begin{pmatrix}1 & 0 & 0 \\ 0 & e^{i \lambda_{2}} & 0 \\ 0 & 0 & e^{i \lambda_{3}}\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin(\theta_{ij})$, $c_{ij} = \cos(\theta_{ij})$, $0 \leq \theta_{ij} \leq \pi/2$ and $ 0 \leq \lambda_{i},\delta_\mathrm{CP} \leq 2\pi$.

By construction, it provides the unitary transformation between the flavor and mass bases.
Any unitary $3\times3$ matrix can be parametrized using three angles and six phases. However, not all phases affect the 
charged and weak currents and are thus not observable by us. Moreover, both the Lagrangian and the currents are invariant under global $U(1)$ transformations,
leaving only one physical phase for us to measure: one term in the form of a Dirac CP-violating phase $\delta_\mathrm{CP}$.
However, if the neutrinos are Majorana fermions, the rephasing of the left-handed fields would cause the neutrino masses to become complex.
Thus, we include two Majorana phases $\lambda_{2},\lambda_3$ in the PMNS matrix. These two phases are detectable in processes that violate lepton number, such as neutrinoless double $\beta$ decay.
Majorana phases are not detectable in neutrino oscillation experiments because oscillations are not violating lepton number.

@@

The three-neutrino oscillation Hamiltonian from Eq.~\eqref{eq:H_3gen}
now reduces to 
\begin{align}
    H_F &= \frac{1}{2E}(U M^2 U^\dagger + A) \nonumber \\
        &= \frac{1}{2E}\left[U \begin{pmatrix}
            0 & 0 & 0 \\
            0 & \dm_{21} & 0 \\
            0 & 0 & 0
        \end{pmatrix} U^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
            1 & 0 & 0 \\
            0 & 0 & 0 \\
            0 & 0 & 0
        \end{pmatrix}\,. 
\end{align}
% The rotation matrices $R_{ij}$ that constitute $U$ according to Eq.~\eqref{PMNS_def} can be simplified. The rotation $R_{13}$ will not affect our mass matrix, since the former acts in the $1-3$ plane, and the latter sits in the $1-2$ plane. Thus, the reduced mass matrix $\mathbb{M}_{12}$ commutes with $R_{13}$. Analogously, the  rotation matrix $R_{23}$ also commutes with $\mathbb{M}_{12}$.
% Moreover, since $SO(3)$ is abelian, its generators commute, i.e.
% \begin{align}
%     \commutator{R_{ij}}{R_{kl}} = R_{ij}R_{kl} - R_{kl}R_{ij} = 0\,.
% \end{align}
% Thus,
% \begin{align}
%     U \mathbb{M}_{12} U^\dagger &=
%     R_{23}R_{13}R_{12} \mathbb{M}_{12}  R_{12}^\dagger R_{13}^\dagger  R_{23}^\dagger \nonumber \\
%     &= R_{12}R_{23}R_{13} \mathbb{M}_{12}  R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger   \nonumber \\
%     &= R_{12}\mathbb{M}_{12} R_{23} R_{13}   R_{13}^\dagger R_{23}^\dagger R_{12}^\dagger  \,.
% \end{align}
% And due to the fact that the rotation matrices are unitary,
% \begin{align}
%     R\,R^\dagger = \mathbb{I}\,,
% \end{align}
% we have that 
% \begin{align}
%     U \mathbb{M}_{12} U^\dagger &= R_{12}\mathbb{M}_{12}R_{23} R_{13}   R_{13}^\dagger R_{12}^\dagger  R_{23}^\dagger \nonumber \\
%     &= R_{12}\mathbb{M}_{12}R_{23} R_{23}^\dagger  R_{12}^\dagger \nonumber \\
%     &= R_{12}\mathbb{M}_{12}  R_{12}^\dagger\,.
% \end{align}
% We have now completely removed the dependence of the mixing angle between the $\nu_1$ and $\nu_3$ mass eigenstates, $\theta_{13}$, and the dependece of the mixing angle between the $\nu_2$ and $\nu_3$ mass eigenstates, $\theta_{23}$.
% We can see this clearly by writing our reduced mixing matrix, which is only constituted by the rotation in the $1-2$ plane, $R_{12}$.
% \begin{align}
%     U &= R_{12}
% \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix} 
% \end{align}

% Let us return to the Hamiltonian with our two-neutrino mixing matrix. We have 
% \begin{align}
%     H_F
%         &= \frac{1}{2E}\left[R_{12} \begin{pmatrix}
%             0 & 0 & 0 \\
%             0 & \dm_{21} & 0 \\
%             0 & 0 & 0
%         \end{pmatrix} R_{12}^\dagger\right] + \sqrt{2}G_F N_e \begin{pmatrix}
%             1 & 0 & 0 \\
%             0 & 0 & 0 \\
%             0 & 0 & 0
%         \end{pmatrix} \nonumber \\
%         &= \frac{1}{2E}\left[\begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}  \begin{pmatrix}
%             0 & 0 & 0 \\
%             0 & \dm_{21} & 0 \\
%             0 & 0 & 0
%         \end{pmatrix} \begin{pmatrix}c_{12} & s_{12} & 0 \\ -s_{12} & c_{12} & 0 \\ 0 & 0 & 1 \end{pmatrix}^\dagger \right] + \sqrt{2}G_F N_e \begin{pmatrix}
%             1 & 0 & 0 \\
%             0 & 0 & 0 \\
%             0 & 0 & 0
%         \end{pmatrix}\,. 
% \end{align}
% TODO: segue into 2gen
We can reduce this down to two dimensions by extracting the upper-left block of all matrices. We now have the Hamiltonian in a two-dimensional form, and start simplifying:

@@

\subsection{Earth propagation}
We now need to know how the electrons are distributed within the Earth. The Preliminary Earth Reference Model~\cite{PREM} gives us spherically
symmetric piecewise polynomials for the Earth density in \si{\gram\cm^-3} shown in the left panel of Fig.~\ref{fig:potential}.
We note a steep discontinuity at \SI{3480}{\km} where the density is nearly halved. This is the core-mantle boundary and will be visible in our 
oscillations.

Using a value of $Y=0.5$ electron per nucleon, we express the matter potential as
\begin{align}
    V_{CC} &= \sqrt{2}G_F N_e = \sqrt{2}G_F Y N_A \,\rho \nonumber \\
           &= \SI{3.8e-23}{\eV} \times \rho\,,
\end{align}
a low number due to the smallness of $G_F$. This is plotted in the right panel of Fig.~\ref{fig:potential}
\begin{figure}
    %TODO: labels
    \centering
    \includegraphics[width=0.9\textwidth]{figures/potential.pdf}
    \caption{\emph{Left panel:} The spherically symmetric Earth density according to PREM~\cite{PREM}, as of distance from the core.
    \emph{Right panel:} $V_{CC}$ using the PREM density and 1/2 electrons per nucleon.}\label{fig:potential}
\end{figure}

@@

\begin{figure}
    %TODO: labels, caption. Include osc params used. Mention value of L if missing.
    % Compare with vacuum oscillation plot and a two neutrino plot. Then we see for certain E we see matter effects more and for some less.
    \centering
    \includegraphics[width=0.7\textwidth]{figures/oscillations.pdf}
    \caption{}\label{fig:oscillations}
\end{figure}

### 2021-12-10 thesis/tex/sterileResults.tex
update

% \begin{document}
\section{The Sterile Hypothesis}\label{sec:sterileResults}
With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
    \caption{How the null hypothesis compares to the IceCube data from~\cite{IC2020}.}\label{fig:IC_rates}
\end{figure}
Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$. Recalling the \si{\TeV} disappearance from 
Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. 
%Thus, we expect the best fitting 
%sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
%that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.

@@

\subsection{Sterile Mass and Mixing}
Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the sterile hypothesis.
The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO:double check these
The contour plot shown in Fig.~\ref{fig:s24_contour} divides the parameter space into two regions.
To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
those parameter pairs can be excluded at a certain confidence level.

@@

We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit sterile hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
sterile hypothesis compares to data.
\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
    \caption{The predicted binned event count assuming our best-fit sterile hypothesis, compared with the 
    null and data.}\label{fig:final_rate_plot}
\end{figure}

%\end{document}

>>>>

% \begin{document}
\section{The Sterile Hypothesis}\label{sec:sterileResults}
% TODO Ch 5.1 write that we didn’t include deep core because resonance doesn’t appear there (in footnote). Refer to figures that show that resonance in TeV. We bring Deepcore back in the next section. 
With the null ($3\nu$) hypothesis normalized to the IceCube Monte Carlo as in Eq.~\ref{eq:Nth}, we are now in good shape to study the sterile effect on the probabilities, and how that compares to data.
First, let us see how the collected data from Fig.~\ref{fig:IC_data} deviates from the predicted $3\nu$ oscillations.
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{figures/IC_rates.pdf}
    \caption{How the null hypothesis compares to the IceCube data from~\cite{IC2020}.}\label{fig:IC_rates}
\end{figure}
Fig.~\ref{fig:IC_rates} shows an impressive agreement to the standard $3\nu$ oscillation picture, with the largest deviations of $~6\%$
for neutrinos with high single-digit \si{\TeV} values. In zenith, the data only deviates $\pm 2\%$. Recalling the \si{\TeV} disappearance from 
Fig.~\ref{fig:sterile_resonance}, we see that we have a similar deficiency found in the data at \SI{4}{\TeV}. 
%Thus, we expect the best fitting 
%sterile hypothesis to include a $\dm[41]$ that places the resonant disappearance in the same region. From Fig.~\ref{fig:resonance_shift}, we see
%that a mass of $\dm[41] = \SI{1.5}{\eV \squared}$ achieves this.

@@

\subsection{Sterile Mass and Mixing}
Let us start with looking at the best-fit event distribution resulting from the $\chi^2$ minimization.
Fig.~\ref{fig:final_rate_plot} now contains the best-fit event distribution assuming the sterile hypothesis.
The best-fit values are $\dm[41] = \SI{0.01}{\eV\squared}$ and 
$\sin(2\theta_{24})^2 = 0.67$ ($\theta_{24} = \SI{27.5}{\degree}$). %TODO:double check these
The contour plot shown in Fig.~\ref{fig:error_tuning} divides the parameter space into two regions.
To the right of the boundary, the $\Delta \chi^2$ has values above the confidence level, meaning that 
those parameter pairs can be excluded at a certain confidence level.

@@

We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit sterile hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
sterile hypothesis compares to data.
\begin{figure}
    %TODO: Fig 5.3 mention what is written in the legend. 
    \centering
    \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
    \caption{The predicted binned event count assuming our best-fit sterile hypothesis, compared with the 
    null and data.}\label{fig:final_rate_plot}
\end{figure}
%TODO: Mention that we see from this that the simulations are consistent with 3+0 with deviations in 6%. Fix label sizes. 
% Include figure on theta34 and say that IC can’t distinguish it.
%\end{document}
